---
title: "Unicef Data Viz"
format: html
editor: visual
---

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:


## The world map represents countries present in the provided data. The colour shifts darker for countries with more knowledge on testing locations.

```{r}

unicef_indicator <- read.csv("./unicef_indicator.csv")

# Load required libraries
library(rnaturalearth)
library(plotly)
library(dplyr)
# Load viridis package for additional color palettes
library(viridis)

# Get a spatial dataset of country boundaries
world_map <- ne_countries(scale = "medium", returnclass = "sf")


main_data <- unicef_indicator
library(rnaturalearth)


merged_data <- world_map %>%
  left_join(main_data, by = c("name" = "country"))


ggplot(data = merged_data) +
  geom_sf(aes(fill = obs_value, text = paste("Obs_value:", obs_value, "<br>Country:", name)), size = 0.1) +
  theme_minimal() +
  scale_fill_viridis_c(option = "A", direction = -1, trans = "log", 
                       name = "Observation\nValue", labels = scales::comma, end = 0.9) +
  labs()



```


## The Bar Chart represents the increase in awareness among men and women for the meantioned period wherein there is a clear growith in awareness regaring the testing centres.

```{r}
library(ggplot2)


data = unicef_indicator[unicef_indicator$time_period > 2003 & unicef_indicator$time_period < 2012, ]

ggplot(data, aes(x=time_period, y=obs_value, fill = sex)) +
  geom_bar(position = "stack",
           stat = "summary",
           fun = "mean")

```

## Scatter Plot: The scatter plot depicts the pattern of changes in awareness for all the countries provided in the data set and depcts changes over the years. There was a rise till 2011 and a dip duriung and after 2012. The possible reason could be the reduction in positive HIV cases and necessary sex education promoted.

```{r}
library(ggplot2)
library(dplyr)

ggplot(unicef_indicator,aes(x=as.numeric(time_period),y=as.numeric(obs_value))) +
  geom_point(color='red') +
  geom_smooth(method = 'lm') +
  xlab("Year") + ylab("Observation Value")
  

```



## The time series chart provided shows the difference in observation values over the years for the list of countries for which the data has been provided.

```{r}
library(ggplot2)
library(dplyr)


ggplot(unicef_indicator, aes(x=as.numeric(time_period), y=as.numeric(obs_value), group = country, colour = country)) +
  geom_line()


```
